Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-07 paper/paper.tex
working draft
working table

\begin{table}[h]
\begin{tabular}{|l|l|l|l|}
    \hline
        Apple  & i     & Apple     & apple        \\
        iphone & apple & iphone    & Apple        \\ 
        i      & the   & ...       & ...          \\ 
        the    & Apple & ipad      & mac          \\ 
        to     & and   & ipod      & juice        \\ 
        my     & to    & rt        & rt           \\ 
        a      & a     & \#apple    & post        \\ 
        ...    & ...   & 5         & new\_post    \\ 
        on     & for   & iphone\_5  & iphone      \\ 
        for    & new   & my\_iphone & apple\_juice \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table*}[ht]
\centering
%\small
\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|c|}{\textbf{Twitter-aware tokenizer}} & \multicolumn{4}{|c|}{\textbf{alphanumeric\_ tokenizer}} & \multicolumn{4}{|c|}{\textbf{whitespace tokenizer}} \\
\hline
\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}} &\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}} &\multicolumn{2}{|c|}{\textbf{no removal}} & \multicolumn{2}{|c|}{\textbf{stopword removal}}\\
\hline
\textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} & \textbf{apple} & \textbf{none} \\ \hline
  Apple  & i     & Apple      & apple        & t        & t     & Apple  & http   & Apple  & apple & Apple   & apple  \\
  iphone & apple & iphone     & Apple        & co       & co    & http   & apple  & to     & I     & iPhone  & Apple  \\
  i      & the   & ...        & ...          & Apple    & http  & iPhone & Apple  & I      & the   & -       & -      \\
  the    & Apple & ipad       & mac          & http     & I     & iPad   & Mac    & the    & Apple & RT      & Mac    \\
  to     & and   & ipod       & juice        & I        & apple & RT     & ED     & my     & to    & iPad    & RT     \\ 
  my     & to    & rt         & rt           & to       & Apple & apple  & juice  & a      & and   & iPod    & juice  \\
  a      & a     & \#apple    & post         & the      & the   & iPod   & RT     & iPhone & a     & 5       & \&     \\
  ...    & ...   & 5          & new\_post    & iPhone   & to    & 5      & iPhone & for    & for   & iphone  & iPhone \\
  on     & for   & iphone\_5  & iphone       & my       & and   & iphone & post   & on     & -     & apple   & post:  \\
  for    & new   & my\_iphone & apple\_juice & a        & a     & ED     & A0     & and    & my    & \#apple & I'm    \\ \hline
\end{tabular}
\caption{Ten most common features for various pipelines.}
\end{table*}

This table of most common features for various pipelines shows the large effect that preprocessing steps like stopword removal, capitalization normalization, bigramming, and tokenization have on the feature distribution. It is interesting that `...' appears as a very common feature using our Twitter-aware tokenizer.
